Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Populations.

### 2023-07-21 src/sections/fidanka.tex
Major progress on injection recovery test section

>>>>

Each population was generated using either a salpeter initial mass function \citep{Salpeter1955} or the initial mass function given in \citep{Milone2012} ($\alpha=-1.2$ redmost population and $\alpha=-0.9$ for the bluemost and second bluemost populations). Every population was assumed to have a binary population fraction of 10\%, to have a distance of 0pc and to have a B-V color excess of 0. Finally, each synthetic population was generated using a fixedf age of 12 Gyr.

\begin{table}
\end{table}

The top panel Figure \ref{} shows the populations generated for these tests. while the bottom panel shows the populations with the density variations highlighted.

We measure the fiducial lines in these populations using \fidanka's fiducial measurment utility. For the same
reasons as outlines in Section \ref{} we use the F275W and F814W filters. A maximum population number is set at 5 for each trial. Figure \ref{} shows the fiducual lines on top of each synthethic population. Recall from Section \ref{} that use of Baysian Gaussian Mixture Modeling (BGMM) allows us to predict the optimal number of populations to recreate a distribution; therefore, where you see a single line BGMM has predicted only one population is needed whereas when you see 2 lines BGMM has preicted that 2 populations are needed. Importantly, these population numbers are not hard coded into our injection and recovery tests.

The efficacy of the fiducual measurment it evaluated by calculating the $\chi^{2}$ metric between the fiducial line and isochrone over 0.1 mag bins. This allows us to probe which portions of the evolutionary sequence contribute most to the overall $\chi^{2}$ difference (Figure \ref{}).
